Andres Karjus

### 2022-07-20 index.Rmd
ic2s2

<div style="text-align: justify; padding-left:1px"> 
I am a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, working on **language and culture dynamics**, using large corpora, machine learning, and human experiments. Recently I have been also working on, through various collaborations, on art history and creative industries and advising collaborative projects between involving academic and media industry partners.<br>
I defended my PhD in 2020, in linguistics at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of University of Edinburgh, on lexical dynamics and communicative need in language.
I also occasionally teach **stats and data visualization** for the humanities and social sciences (see [more here](https://andreskarjus.github.io/artofthefigure)). On the right is the (of course slightly outdated) photo, obligatory for all academic home pages, to subtly suggest that in fact I do not spend _all_ my time in the office at all.

@@

- Seminar talk at the Poncelet laboratory in Moscow (November 2021)
- [Conference on Complex Systems 2021](https://ccs2021.univ-lyon1.fr/) (October 2021) | [slides](https://andreskarjus.github.io/talks/ccs2021/Karjus_CCS2021_Capturing_aesthetic_complexity.pdf)
- [Protolang 7](https://blogs.phil.hhu.de/protolang7/programme/) (September 2021) | [slides](https://andreskarjus.github.io/talks/andres_karjus_protolang7.pdf)
- [Culture Conference 2021](https://culture-conference.com/) | [Poster on aesthetic complexity](https://andreskarjus.github.io/talks/cultureconference2021/)
- [TÜling](https://www.keel.ut.ee/et/tuling) (April 2021)
- [Colloquium for Computational Linguistics and Linguistics in Stuttgart](https://www.ims.uni-stuttgart.de/en/research/colloquium/) | [Slides](https://andreskarjus.github.io/talks/stuttgart2021/andres_karjus_lexical_dynamics_slides_stuttgart2021.pdf) | [Recording](https://www.ims.uni-stuttgart.de/documents/aktuelles/veranstaltungen/210111-Karjus-Talk-Colloq-Recording.mp4)
- [RUSE 2019](http://rusesymposium.org.uk/). Slides [here](https://andreskarjus.github.io/ruse2019).
- [CL2019](http://www.cl2019.org/). Slides [here](https://andreskarjus.github.io/cl2019talk.html).
- [Culture Conference 2019](https://culture-conference.com/programme-2019/), Poster [here](https://andreskarjus.github.io/lexcom_poster).
- [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html) | _Modelling lexical interactions in diachronic corpora_ |  [poster](https://andreskarjus.github.io/isle_poster)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)
- Corpus Linguistics in Scotland Network Meeting, _Topical Fluctuations and Lexical Interactions in Diachronic Corpora_

>>>>

<div style="text-align: justify; padding-left:1px"> 
I am a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, working on **language and culture dynamics**, using large corpora, machine learning, and human experiments. Recently I have been also working on, through various collaborations, on art history and creative industries and advising collaborative projects between involving academic and media industry partners.<br>
I defended my PhD in 2020, in linguistics at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of University of Edinburgh, on lexical dynamics and communicative need in language.
I also occasionally teach **stats and data visualization** for the humanities and social sciences (see [more here](https://andreskarjus.github.io/artofthefigure)). The photo on the right naturally slightly outdated, as is customary on academic home pages.

@@

- Poster "Linguistic divergence in American English along socio-political polarities", the [IC2S2](https://www.ic2s2.org/) Computational Social Science Conference (20.07.2022) | [pdf](https://andreskarjus.github.io/talks/ic2s2/IC2S2_poster_Linguistic_divergence_in_American_English_along_socio-political_polarities.pdf)
- Seminar talk at the Poncelet laboratory in Moscow (November 2021)
- [Conference on Complex Systems 2021](https://ccs2021.univ-lyon1.fr/) (October 2021) | [slides](https://andreskarjus.github.io/talks/ccs2021/Karjus_CCS2021_Capturing_aesthetic_complexity.pdf)
- [Protolang 7](https://blogs.phil.hhu.de/protolang7/programme/) (September 2021) | [slides](https://andreskarjus.github.io/talks/andres_karjus_protolang7.pdf)
- [Culture Conference 2021](https://culture-conference.com/) | [Poster on aesthetic complexity](https://andreskarjus.github.io/talks/cultureconference2021/)
- [TÜling](https://www.keel.ut.ee/et/tuling) (April 2021)
- [Colloquium for Computational Linguistics and Linguistics in Stuttgart](https://www.ims.uni-stuttgart.de/en/research/colloquium/) | [Slides](https://andreskarjus.github.io/talks/stuttgart2021/andres_karjus_lexical_dynamics_slides_stuttgart2021.pdf) | [Recording](https://www.ims.uni-stuttgart.de/documents/aktuelles/veranstaltungen/210111-Karjus-Talk-Colloq-Recording.mp4)
- [RUSE 2019](http://rusesymposium.org.uk/). Slides [here](https://andreskarjus.github.io/ruse2019).
- [CL2019](http://www.cl2019.org/). Slides [here](https://andreskarjus.github.io/cl2019talk.html).
- [Culture Conference 2019](https://culture-conference.com/programme-2019/), Poster [here](https://andreskarjus.github.io/lexcom_poster).
- [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html) | _Modelling lexical interactions in diachronic corpora_ |  [poster](https://andreskarjus.github.io/isle_poster)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)
- Corpus Linguistics in Scotland Network Meeting, _Topical Fluctuations and Lexical Interactions in Diachronic Corpora_

### 2022-07-20 news.Rmd
news
ic2s2

>>>>

- Poster "Linguistic divergence in American English along socio-political polarities", at the [IC2S2](https://www.ic2s2.org/) Computational Social Science Conference in Chicago (20.07.2022) | [pdf](https://andreskarjus.github.io/talks/ic2s2/IC2S2_poster_Linguistic_divergence_in_American_English_along_socio-political_polarities.pdf)

- New preprint: "Compression ensembles quantify aesthetic complexity and the evolution of visual art" https://arxiv.org/abs/2205.10271
